---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Abigail Zysk"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 variables in the datasaurus_dozen file. 

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient between x and y for this dataset is -0.06447

### Exercise 3


```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

The resulting plot is a star

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The correlationn between x and y for the star dataset is -0.06296, this value is really similar to the correlation coefficent of dino.

### Exercise 4


```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The resulting plot is a oval

```{r}
circle_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficent between x and y for the circle data set is -0.06834, the value is similar to the correlation coefficents of the star and dino datasets bet a little more negatively correlated.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)